---
title: "fig5_PolysaccharideMuribac"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

setwd("~/Dropbox/fmt/scripts/")
library(tidyverse)
library(wesanderson)
library(ggthemes)
library(data.table)
library(tidytext)
library(cowplot)
source("CompteSpearmanCorrelationAndMelt.R")


ven <- c('#FAAF40',"#1B75BB","#37B34A", "#F05A28")
pal <- wes_palette("Zissou1", 100, type = "continuous")


options(stringsAsFactors = F)
options(scipen = 10000)

CorrectedData <- data.table::fread("~/Dropbox/fmt/experiments/2022-09-13 Guillaume FMT r3/CorrectedDataFrame.csv")
Tax_Table <- data.table::fread("~/Dropbox/fmt/experiments/2022-09-13 Guillaume FMT r3/SilvaTax.csv")
otumapping <- read.csv("../experiments/2022-09-13 Guillaume FMT r3/DeSeq_OTU_dynamics.csv")
subgroups <- read.csv('../tables/OTUSubgroups.csv') %>% mutate(subgroup =as.factor(subgroup), 
                                                               OTU = paste('Otu',OTU, sep = ''))


```



#Assemble all prevalent sets
```{r}

PrevalentSets <- rbind((read.csv("../experiments/2022-09-13 Guillaume FMT r3/PrevalentSet_noclust1_Env2Jax.csv") %>% 
  mutate(MouseGroup = 'Env2Jax')),
(read.csv("../experiments/2022-09-13 Guillaume FMT r3/PrevalentSet_noclust1_Jax.csv") %>% 
  mutate(MouseGroup = 'Jax')),
(read.csv("../experiments/2022-09-13 Guillaume FMT r3/PrevalentSet_noclust1_Env.csv") %>% 
  mutate(MouseGroup = 'Env'))) %>% select(-X) %>% mutate(MouseGroup = as.factor(MouseGroup)) %>%
    group_by(MouseGroup) %>% 
  mutate(Zscore = ifelse(is.infinite(Zscore), max(Zscore[!is.infinite(Zscore)]), Zscore)) %>% ungroup()

#Bound Zscores if negative
#PrevalentSets$Zscore[PrevalentSets$Zscore < -1e6] <- -16

```

5A - Env2Jax
```{r}

group <- 'Env2Jax' #can change to other mouse groups too

#Need to duplicate df to mirror heatmap
PrevalentSet <-
  rbind(
  read.csv(
     paste("../experiments/2022-09-13 Guillaume FMT r3/PrevalentSet_noclust1_",group, ".csv", sep = '')) %>%
    #filter(Order_OTU1 == 'Bacteroidia' | Order_OTU1 == 'Clostridia') %>%
    select(OTU1ColorName, OTU2ColorName, Zscore, Significant, Class_OTU1, Order_OTU1) %>% distinct(),
     read.csv(
       paste("../experiments/2022-09-13 Guillaume FMT r3/PrevalentSet_noclust1_",group, ".csv", sep = '')) %>%
    #filter(Order_OTU2 == 'Bacteroidia'  | Order_OTU2 == 'Clostridia') %>%
    select(OTU1ColorName, OTU2ColorName, Zscore, Significant, Class_OTU2, Order_OTU2) %>% distinct() %>%
   rename(c("OTU1ColorName"="OTU2ColorName", "OTU2ColorName"="OTU1ColorName", "Class_OTU1"="Class_OTU2", "Order_OTU1"="Order_OTU2"))) %>%
  mutate(Zscore = ifelse(is.infinite(Zscore), max(Zscore[!is.infinite(Zscore)], na.rm = TRUE), Zscore)) %>% ungroup()

temp <- read.csv("../misc/bugColors_MapsSeq.csv")
bugColors<- setNames(c(scales::hue_pal()(length(unique(temp$X)))), c(levels(as.factor(temp$X)))) 

PrevalentSet.cast <- PrevalentSet %>%
  filter(OTU1ColorName != 'NA') %>% 
  select(OTU1ColorName, OTU2ColorName, Zscore) %>% distinct() %>% 
  reshape2::dcast(OTU1ColorName~OTU2ColorName)

#clustering
PrevalentSet.cast.matrix <- as.matrix(PrevalentSet.cast[, -c(1)])
#PrevalentSet.cast.matrix[is.infinite(PrevalentSet.cast.matrix)] <- 50

rownames(PrevalentSet.cast.matrix) <- PrevalentSet.cast$OTU1ColorName
PrevalentSet.cast.dendro <- as.dendrogram(hclust(d = dist(x = PrevalentSet.cast.matrix), method = "ward"))
PrevalentSet.cast$order <- order.dendrogram(PrevalentSet.cast.dendro)
  
#which clustering method strongest...
# methods to assess 
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")

# function to compute coefficient
ac <- function(x) {
  cluster::agnes(PrevalentSet.cast.matrix, method = x)$ac
}

map_dbl(m, ac)
#ward strongest clusterer


# Create dendro
dendro.plot <- ggdendro::ggdendrogram(data = PrevalentSet.cast.dendro, 
                            rotate=FALSE) + 
                  coord_flip() + scale_y_reverse() + scale_x_reverse() + 
                  theme(axis.line = element_blank(),
                        axis.text = element_blank()) + theme_void()

# Preview the plot
print(dendro.plot)

PrevalentSet.cast.long <- reshape2::melt(PrevalentSet.cast, id = c("OTU1ColorName", "order")) %>% distinct()

#reorder
#PrevalentSet.cast.order <- order.dendrogram(PrevalentSet.cast.dendro)
PrevalentSet.cast.long$OTU1ColorName <- factor(x = PrevalentSet.cast.long$OTU1ColorName,
                               levels = PrevalentSet.cast$OTU1ColorName[PrevalentSet.cast$order], 
                               ordered = TRUE)

temp <- PrevalentSet.cast.long %>% 
          select(OTU1ColorName, OTU2ColorName=variable, Zscore = 'value') %>% 
          left_join(., 
            (PrevalentSet %>% 
               select(OTU1ColorName, OTU2ColorName, Significant, 
                      Order_OTU1)), 
            by = c("OTU1ColorName", "OTU2ColorName")) %>% 
          left_join(., select(PrevalentSets, OTU1, OTU1ColorName)) %>% distinct() %>%
          left_join(., select(otumapping, OTU1=OTU, log2FoldChange, emergence)) %>% distinct()

y_min <- round(min(temp$Zscore, na.rm = T),digits = -1)
y_max <- round(max(temp$Zscore, na.rm = T),digits = -1)

clustr <- temp %>% 
                 ggplot(aes(x = OTU1ColorName, y = OTU2ColorName, fill = Zscore)) +
  geom_tile(color = 'white') +
  scale_fill_gradient2(low="blue", high="darkred",midpoint = 0, breaks = seq(y_min, y_max, by = (y_max-y_min)/5)) + #,limits=c(-.5,.5)) +
  theme_clean() +
  scale_y_discrete(limits = rev(PrevalentSet.cast.long$OTU1ColorName[PrevalentSet.cast$order])) +
  scale_x_discrete(limits = rev(PrevalentSet.cast.long$OTU1ColorName[PrevalentSet.cast$order])) +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 90, vjust = 0.35, hjust=1, size = 10),
    axis.text.y = ggtext::element_markdown()) +
  labs(fill = "Co-Assoc.\nScore")  +
  xlab("OTU X") +
  ylab("OTU Y") +
  geom_point(data=function(x){x[temp$Significant == TRUE, ]},size=.2,color="black", fill = 'black')
    #geom_point(data=function(x){x[temp$Significant == TRUE & temp$Zscore > 0, ]},
    #           size=.6,color="black", fill = 'black', shape = 16) +
    #geom_point(data=function(x){x[temp$Significant == TRUE & temp$Zscore < 0, ]},
    #           size=.6,color="black", fill = 'black', shape = 17)



corplot_fam <- PrevalentSet %>%  
  ggplot(.,aes(OTU1ColorName, y = 1, fill = Class_OTU1)) +
                 geom_tile(color = 'black') + theme_clean() +
    scale_x_discrete(limits = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) +
  scale_fill_manual(values = bugColors) +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 90, vjust = 0.2, hjust=1, size = 8),
    axis.text.y = ggtext::element_markdown(size = 8)) +
  labs(fill = "Class", x = "OTU 1") 

corplot_fam

corplot_fc <- temp %>%  
  ggplot(.,aes(OTU1ColorName, y = 1, fill = emergence)) +
                 geom_tile(color = 'black') + theme_clean() +
    scale_x_discrete(limits = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) +
  scale_fill_manual(values = c('#000000','#ff0000', 'grey80')) +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 90, vjust = 0.35, hjust=1, size = 8),
    axis.text.y = ggtext::element_markdown(size = 8)) +
  labs(fill = "Class", x = "OTU 1") 

ggsave(paste("../figs/fig5/", group, "/emergence_mapSeq_", group, ".pdf",sep = ''), corplot_fc,width = 6, height = 1.5)

#OTU1 missing from these...
corplot_type <- data.frame(OTU1ColorName = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) %>%
  left_join(., select(PrevalentSets, OTU1ColorName, OTU1Type) %>% distinct(), by = 'OTU1ColorName') %>%
    mutate(OTU1Type= ifelse(OTU1ColorName == "<b style='color:#377EB8'>Otu1", 'Shared Taxa', OTU1Type)) %>%
  ggplot(.,aes(OTU1ColorName, y = 1, fill = OTU1Type)) +
                 geom_tile(color = 'black') + theme_clean() +
    scale_x_discrete(limits = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) +
  scale_fill_manual(values = c('#377EB8', '#E41A1C','#828382')) +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 90, vjust = 0.35, hjust=1, size = 8),
    axis.text.y = ggtext::element_markdown(size = 8)) +
  labs(fill = "Class", x = "OTU 1") 
corplot_type

subgroup_type <- data.frame(OTU1ColorName = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) %>%
  left_join(., select(PrevalentSets, OTU1ColorName, OTU=OTU1) %>% distinct(), by = 'OTU1ColorName') %>% 
  mutate(OTU= ifelse(OTU1ColorName == "<b style='color:#377EB8'>Otu1", 'Otu1', OTU)) %>%
  left_join(., subgroups) %>% na.omit() %>% mutate(subgroup = paste('Subgroup', subgroup)) %>%
  ggplot(.,aes(OTU1ColorName, y = 1, fill = subgroup)) +
                 geom_tile(color = 'black') + theme_clean() +
    scale_x_discrete(limits = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) +
  scale_fill_manual(values = c('#3b4d81', '#8967ac','#5aadc5', '#54b948')) +
  labs(x='', y='', fill='Spatial Subgroup') +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 90, vjust = 0.35, hjust=1, size = 8),
    axis.text.y = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(), legend.position = 'top') +
  labs(fill = "Class", x = "OTU 1") + facet_wrap(~MouseGroup,nrow = 2)

subgroup_type
ggsave(paste("../figs/fig5/", group, "/subgroup_mapSeq_", group, ".pdf",sep = ''), subgroup_type,width = 4.5, height = 3)


ggsave(paste("../figs/fig5/", group, "/type_mapSeq_", group, ".pdf",sep = ''), corplot_type, 
       width = 6, height = 1.5)

cowplot::plot_grid(dendro.plot, clustr, corplot_fam, nrow = 1, rel_widths = c(.25, 1, 1))



ggsave(paste("../figs/fig5/", group, "/5AMaPSSeq_order_noclust1_", group, ".pdf",sep = ''), width = 15, height = 5.5)


#interesting for later.... Colonizing OTUs are not most abundant
temp <- data.frame(OTU1ColorName = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) %>%
  left_join(., select(PrevalentSets, MouseGroup, OTU1ColorName, OTU1, OTU1Type, InstancesOTU1)) %>% distinct() %>% filter(MouseGroup == group) %>% 
  left_join(., otumapping, by = c('OTU1' = 'OTU')) %>% distinct() %>% 
  left_join(., read.csv("../tables/Instances_MaPS-Seq.csv") %>% select('OTU1'='OTU',MouseGroup,prop_OTU) %>% filter(MouseGroup == group)) %>%
  ggplot(.,aes(OTU1ColorName)) +
       # geom_tile(aes(y=1, fill = log10(prop_OTU))) +
       geom_bar(color = 'black', stat = 'identity', aes(y = log10(prop_OTU))) + theme_minimal() +
    scale_x_discrete(limits = rev(PrevalentSet.cast.long$OTU1[PrevalentSet.cast$order])) +
  viridis::scale_fill_viridis() +
  theme(
    axis.text.x = ggtext::element_markdown(angle = 90, vjust = 0.35, hjust=1, size = 8),
    axis.text.y = element_blank(), plot.background = element_blank(), 
    axis.ticks = element_blank()) +
  labs(fill = "Class", x = "OTU 1") 

temp

ggsave(paste("../figs/fig5/", group, "/abundance_", group, ".pdf",sep = ''), width = 6, height = 1.5)

```


abundance of different subgroups?
```{r}

temp <- read.csv('../tables/OTUSubgroups.csv') %>% 
      mutate(OTU = paste('Otu', OTU, sep = '')) %>% 
      left_join(read.csv("../tables/Instances_MaPS-Seq.csv")) 

temp %>% #mutate(prop_OTU = log10(prop_OTU/100)) %>%
    ggplot(., aes(MouseGroup, prop_OTU, fill = MouseGroup)) + 
  geom_boxplot() + geom_jitter() + facet_wrap(~subgroup, scales = 'free') + theme_cowplot()


#subgroup 2 is significant
wilcox.test(filter(temp, MouseGroup == 'Env' & subgroup == '2')$prop_OTU,
            filter(temp, MouseGroup == 'Jax' & subgroup == '2')$prop_OTU, alternative = 'greater')

wilcox.test(filter(temp, MouseGroup == 'Jax' & subgroup == '4')$prop_OTU,
            filter(temp, MouseGroup == 'Env' & subgroup == '4')$prop_OTU, alternative = 'greater')

```

#5c? Make network diagram of mean bacteroides interactions, show present nodes arranged in auto


FOR BACTEROIDALES   Jax (A) COLOR_FLIPPED
```{r}

library(ggraph)
library(igraph)

bugColors <- setNames(c(scales::hue_pal()(length(unique(PrevalentSets$Family_OTU1)))), c(levels(as.factor(PrevalentSets$Family_OTU1))))

#average interactions 
mean_interactions <- PrevalentSets %>%
  filter(zpadjusted < .01) %>% 
  mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative')) %>% 
  select(OTU1, OTU2, Zscore, zpadjusted,interaction,MouseGroup, 
         Class_OTU1, Family_OTU1, Class_OTU2, Family_OTU2, OTU1Type, OTU2Type)%>% 
  distinct %>% ungroup()

#Count OTU instances
Instances <- rbind(PrevalentSets %>% select(MouseGroup, OTU1, Instances=InstancesOTU1) %>% distinct(),
                   PrevalentSets %>% select(MouseGroup, OTU1=OTU2, Instances=InstancesOTU2) %>% distinct()) %>% 
  group_by(MouseGroup, OTU1) %>% mutate(total_instances = (sum(Instances))) %>% ungroup() %>% 
  select(OTU1, MouseGroup, total_instances) %>% distinct() %>% 
  mutate(OTU1 = gsub('Otu', '', .$OTU1))

#Let's try when we count instances immediately
Instances_new <- read.csv("../tables/Instances_MaPS-Seq.csv") %>% 
    select(OTU1=OTU, prop_OTU, MouseGroup, Order, Family, alpha) %>%
    mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% distinct()


#tbl_nodes[unique(tbl_nodes$Class_OTU1) %in% unique(PrevalentSet$Class_OTU1),]
#unique(tbl_nodes$Class_OTU1) %in% unique(PrevalentSet$Class_OTU1)


# Create data frame for edges

cluster_network <- PrevalentSets %>% #left_join(., Instances, by = c("OTU1", "MouseGroup")) %>%
  left_join(., data.frame(OTU1Type = c("Env Taxa", 'Recipient Taxa', 'Shared Taxa'), 
                            Color = c('#377Ebb', '#E41A1C','#828382'))) %>%
  mutate(OTU1 = gsub('Otu', '', .$OTU1),
         OTU2 = gsub('Otu', '', .$OTU2)) #only significant interactions




#Make dummy edges
tbl_edges_all <- cluster_network %>% 
  filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
    select(OTU1, OTU2, Class_OTU1,Class_OTU2) %>% 
    #mutate(interaction = 1) %>% 
    distinct()

edges <- rbind(select(tbl_edges_all,OTU1, Class_OTU1), select(tbl_edges_all, OTU1=OTU2, Class_OTU1=Class_OTU2)) %>% distinct()


#create node information
tbl_nodes_all <- cluster_network %>% 
  filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
  select(OTU1, Class_OTU1) %>%
  distinct() %>% left_join(edges,.) %>%   
  mutate(OTU1 = as.numeric(OTU1)) %>%
  arrange(OTU1) %>% mutate(OTU1 = as.character(OTU1)) %>% distinct()
# %>%filter(OTU1 != '81' & OTU1 != '84') #remove OTUs in Env but not others...




# - FMT


#Now layer edges for -FMT
tbl_edges<- cluster_network %>% filter(MouseGroup == 'Jax' & Significant == T) %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
      select(OTU1, OTU2, Zscore, zpadjusted) %>% 
    mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative'),
           zpadjusted=log10(1/zpadjusted)) %>%
    select(OTU1, OTU2, interaction, Zscore) %>%
    #left_join(tbl_edges_all, ., by = c('OTU1','OTU2')) %>%
    replace(is.na(.), 0) %>%
    distinct()


#Get nodes found in -FMT

tbl_nodes <- rbind(cluster_network %>% filter(MouseGroup == 'Jax') %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% select(OTU1, Family_OTU1)%>% distinct(),
    cluster_network %>% filter(MouseGroup == 'Jax') %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
   mutate(OTU2 = gsub('Otu', '', .$OTU2)) %>% select(OTU1=OTU2, Family_OTU1=Family_OTU2)%>% distinct()) %>% 
    mutate(alpha = 1) %>% distinct() %>% left_join(., filter(Instances, MouseGroup == 'Jax'), by = 'OTU1') %>%
    select(-MouseGroup) %>% mutate(total_instances = as.numeric(total_instances)) %>%
  left_join(tbl_nodes_all, ., by = 'OTU1') %>% 
  mutate(Family_OTU1 = ifelse(is.na(Family_OTU1), 'Undetermined', Family_OTU1)) %>%
  replace(is.na(.), .01) %>% distinct() %>% select(-alpha) %>%
  left_join(., filter(Instances_new, MouseGroup == 'Jax'))

#Find missing taxa & remove their edges
missing_taxa <- tbl_nodes %>% filter(alpha == .01) %>% select(OTU1) %>% mutate(OTU2=OTU1)

tbl_edges <- tbl_edges %>% anti_join(., missing_taxa, 'OTU1') %>% anti_join(., missing_taxa, 'OTU2')

#How many negative interactions from 28, 21, or 76?
nrow(filter(filter(tbl_edges, interaction == 'Negative'), OTU1== 28 | OTU2 == 28))
nrow(filter(filter(tbl_edges, interaction == 'Negative'), OTU1== 21 | OTU2 == 21))
nrow(filter(filter(tbl_edges, interaction == 'Negative'), OTU1== 76 | OTU2 == 76))
nrow(filter(filter(tbl_edges, interaction == 'Negative'), OTU1== 62 | OTU2 == 62))
nrow(filter(filter(tbl_edges, interaction == 'Negative'), OTU1== 99 | OTU2 == 99))



#merge node and edge data
graph_nodes <- graph_from_data_frame(tbl_edges, tbl_nodes, directed = T) %>% 
        delete_vertices(., V(.)$name == 28 | V(.)$name == 62 | V(.)$name == 84)

#graph just nodes
nodes <- ggraph(graph_nodes, layout = 'circle') +
   geom_edge_link(aes(
                      edge_width = abs(Zscore)*.001, 
                       alpha = abs(Zscore), 
                       edge_color = interaction),) +
      scale_edge_width(
                       aes((Zscore)),
                       range = c(.001, 2)
                       ) +
    scale_edge_color_manual(values = c('navyblue', 'firebrick')) + #FLIPPED
  #geom_node_point(aes(size = prop_OTU, alpha = alpha), color = 'black') +
  geom_node_point(aes( size = prop_OTU*.6, color = Family, alpha = alpha)) +
  scale_color_manual(values = bugColors) +
     scale_size(range = c(.001,11)) +
  labs(color = 'Order', 
         title = "Jax") +
    theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'none') 

a <- nodes + geom_node_text(aes(label = name), size = 3,  nudge_x = nodes$data$x * .3, nudge_y = nodes$data$y * .3, check_overlap=FALSE)
a
# Env

#Get nodes found in Env



#Now layer edges for Env
tbl_edges<- cluster_network %>% filter(MouseGroup == 'Env' & Significant == T) %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
      select(OTU1, OTU2, Zscore, zpadjusted) %>% 
    mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative'),
           zpadjusted=log10(1/zpadjusted)) %>%
    select(OTU1, OTU2, interaction, Zscore) %>%
    #left_join(tbl_edges_all, ., by = c('OTU1','OTU2')) %>%
    replace(is.na(.), 0) %>%
    distinct()


#Get nodes found in Env

tbl_nodes <- rbind(cluster_network %>% filter(MouseGroup == 'Env') %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% select(OTU1, Family_OTU1)%>% distinct(),
    cluster_network %>% filter(MouseGroup == 'Env') %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
   mutate(OTU2 = gsub('Otu', '', .$OTU2)) %>% select(OTU1=OTU2, Family_OTU1=Family_OTU2)%>% distinct()) %>% 
    mutate(alpha = 1) %>% distinct() %>% left_join(., filter(Instances, MouseGroup == 'Jax'), by = 'OTU1') %>%
    select(-MouseGroup) %>% mutate(total_instances = as.numeric(total_instances)) %>%
  left_join(tbl_nodes_all, ., by = 'OTU1') %>% 
  mutate(Family_OTU1 = ifelse(is.na(Family_OTU1), 'Undetermined', Family_OTU1)) %>%
  replace(is.na(.), .01) %>% distinct() %>% select(-alpha) %>%
    left_join(., filter(Instances_new, MouseGroup == 'Env'))



#Find missing taxa & remove their edges
missing_taxa <- tbl_nodes %>% filter(alpha == .01) %>% select(OTU1) %>% mutate(OTU2=OTU1)

tbl_edges <- tbl_edges %>% anti_join(., missing_taxa, 'OTU1') %>% anti_join(., missing_taxa, 'OTU2')


#merge node and edge data. remove OTU not found in Env2jax or Jax
graph_nodes <- graph_from_data_frame(tbl_edges, tbl_nodes, directed = T) %>%
        delete_vertices(., V(.)$name == 28 | V(.)$name == 62 | V(.)$name == 84)


#graph just nodes
nodes <- ggraph(graph_nodes, layout = 'circle') +
   geom_edge_link(aes(
                      edge_width = abs(Zscore)*.001, 
                       alpha = abs(Zscore), 
                       edge_color = interaction),) +
      scale_edge_width(
                       aes((Zscore)),
                       range = c(.01, 2)
                       ) +
    scale_edge_color_manual(values = c('navyblue','firebrick')) +
  #geom_node_point(aes(size = prop_OTU, alpha = alpha), color = 'black') +
  geom_node_point(aes( size = prop_OTU*.6, color = Family,alpha = alpha)) +
  scale_color_manual(values = bugColors) +
     scale_size(range = c(.001,11)) +
  scale_color_manual(values = bugColors) +
  labs(color = 'Order', 
         title = "Env") +
    theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'none') 

b <- nodes + geom_node_text(aes(label = name), size = 3,  nudge_x = nodes$data$x * .3, nudge_y = nodes$data$y * .3, check_overlap=FALSE)
b

# +FMT

#Now layer edges for +FMT
tbl_edges<- cluster_network %>% filter(MouseGroup == 'Env2Jax' & Significant == T) %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
      select(OTU1, OTU2, Zscore, zpadjusted) %>% 
    mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative'),
           zpadjusted=log10(1/zpadjusted)) %>%
    select(OTU1, OTU2, interaction, Zscore) %>%
    #left_join(tbl_edges_all, ., by = c('OTU1','OTU2')) %>%
    replace(is.na(.), 0) %>%
    distinct()


#Get nodes found in +FMT

tbl_nodes <- rbind(cluster_network %>% filter(MouseGroup == 'Env2Jax') %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% select(OTU1, Family_OTU1)%>% distinct(),
    cluster_network %>% filter(MouseGroup == 'Env2Jax') %>%
    filter(Class_OTU1 == 'Bacteroidia' & Class_OTU2 == 'Bacteroidia') %>%
   mutate(OTU2 = gsub('Otu', '', .$OTU2)) %>% select(OTU1=OTU2, Family_OTU1=Family_OTU2)%>% distinct()) %>% 
    mutate(alpha = 1) %>% distinct() %>% left_join(., filter(Instances, MouseGroup == 'Jax'), by = 'OTU1') %>%
    select(-MouseGroup) %>% mutate(total_instances = as.numeric(total_instances)) %>%
  left_join(tbl_nodes_all, ., by = 'OTU1') %>% 
  mutate(Family_OTU1 = ifelse(is.na(Family_OTU1), 'Undetermined', Family_OTU1)) %>%
  replace(is.na(.), .01) %>% distinct() %>% select(-alpha) %>%
    left_join(., filter(Instances_new, MouseGroup == 'Env2Jax'))

#Find missing taxa & remove their edges
missing_taxa <- tbl_nodes %>% filter(alpha == .01) %>% select(OTU1) %>% mutate(OTU2=OTU1)

tbl_edges <- tbl_edges %>% anti_join(., missing_taxa, 'OTU1') %>% anti_join(., missing_taxa, 'OTU2')

#merge node and edge data
graph_nodes <- graph_from_data_frame(tbl_edges, tbl_nodes, directed = T) %>%
        delete_vertices(., V(.)$name == 28 | V(.)$name == 62 | V(.)$name == 84)


#graph just nodes
nodes <- ggraph(graph_nodes, layout = 'circle') +
   geom_edge_link(aes(
                      edge_width = abs(Zscore)*.001, 
                       alpha = abs(Zscore), 
                       edge_color = interaction),) +
      scale_edge_width(
                       aes((Zscore)),
                       range = c(.01, 2)
                       ) +
      scale_edge_color_manual(values = c('navyblue', 'firebrick')) + #FLIPPED
    #scale_edge_color_manual(values = c('firebrick')) + #add 'navyblue' if necessary
  #geom_node_point(aes(size = prop_OTU, alpha = alpha), color = 'black') +
  geom_node_point(aes( size = prop_OTU*.6, color = Family, alpha = alpha)) +
  scale_color_manual(values = bugColors) +
     scale_size(range = c(.001,11)) +
  scale_color_manual(values = bugColors) +
  labs(color = 'Order', 
         title = "Env2Jax") +
    theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'none') 


c <- nodes + geom_node_text(aes(label = name), size = 3,  nudge_x = nodes$data$x * .3, nudge_y = nodes$data$y * .3, check_overlap=FALSE)
c

leg <- cowplot::get_legend(ggraph(graph_nodes, layout = 'circle') + 
    geom_edge_link(aes(edge_width = Zscore), alpha =.4) +
    scale_edge_width_continuous(range = c(0,5)) +
    geom_node_point(size = 14, aes(color = Family_OTU1)) +
    scale_color_manual(values = bugColors) +labs(color = 'Order') +
      theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'bottom'))
    

temp <- cowplot::plot_grid(a,c,b,  nrow = 1)
temp
ggsave("../figs/fig5/5E_InteractionNetworks.png", width = 8,height = 2.8)
ggsave("../figs/fig5/5E_InteractionNetworks.pdf", width = 8,height = 2.8)

cowplot::plot_grid(leg)
ggsave("../figs/fig5/5E_InteractionNetworks_leg.png", width = 14,height = 2.8)
ggsave("../figs/fig5/5E_InteractionNetworks_leg.pdf", width = 14,height = 2.8)
cowplot::plot_grid(temp, leg, nrow = 2)
```


FOR Clostridia
```{r}

library(ggraph)
library(igraph)

bugColors <- setNames(c(scales::hue_pal()(length(unique(PrevalentSets$Family_OTU1)))), c(levels(as.factor(PrevalentSets$Family_OTU1))))

#average interactions 
mean_interactions <- PrevalentSets %>%
  filter(zpadjusted < .01) %>% 
  mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative')) %>% 
  select(OTU1, OTU2, Zscore, zpadjusted,interaction,MouseGroup, 
         Class_OTU1, Family_OTU1, Class_OTU2, Family_OTU2, OTU1Type, OTU2Type)%>% 
  distinct %>% ungroup()

#Count OTU instances
Instances <- rbind(PrevalentSets %>% select(MouseGroup, OTU1, Instances=InstancesOTU1) %>% distinct(),
                   PrevalentSets %>% select(MouseGroup, OTU1=OTU2, Instances=InstancesOTU2) %>% distinct()) %>% 
  group_by(MouseGroup, OTU1) %>% mutate(total_instances = (sum(Instances))) %>% ungroup() %>% 
  select(OTU1, MouseGroup, total_instances) %>% distinct() %>% 
  mutate(OTU1 = gsub('Otu', '', .$OTU1))

#Let's try when we count instances immediately
Instances_new <- read.csv("../tables/Instances_MaPS-Seq.csv") %>% 
    select(OTU1=OTU, prop_OTU, MouseGroup, Order, Family, alpha) %>%
    mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% distinct()


#tbl_nodes[unique(tbl_nodes$Class_OTU1) %in% unique(PrevalentSet$Class_OTU1),]
#unique(tbl_nodes$Class_OTU1) %in% unique(PrevalentSet$Class_OTU1)


# Create data frame for edges

cluster_network <- PrevalentSets %>% #left_join(., Instances, by = c("OTU1", "MouseGroup")) %>%
  left_join(., data.frame(OTU1Type = c("Env Taxa", 'Recipient Taxa', 'Shared Taxa'), 
                            Color = c('#377Ebb', '#E41A1C','#828382'))) %>%
  mutate(OTU1 = gsub('Otu', '', .$OTU1),
         OTU2 = gsub('Otu', '', .$OTU2)) #only significant interactions





#Make dummy edges
tbl_edges_all <- cluster_network %>% 
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
    select(OTU1, OTU2, Class_OTU1,Class_OTU2) %>% 
    #mutate(interaction = 1) %>% 
    distinct()

edges <- rbind(select(tbl_edges_all,OTU1, Class_OTU1), select(tbl_edges_all, OTU1=OTU2, Class_OTU1=Class_OTU2)) %>% distinct()


#create node information
tbl_nodes_all <- cluster_network %>% 
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
  select(OTU1, Class_OTU1) %>%
  distinct() %>% left_join(edges,.) %>%   
  mutate(OTU1 = as.numeric(OTU1)) %>%
  arrange(OTU1) %>% mutate(OTU1 = as.character(OTU1)) %>% distinct()



# - FMT


#Now layer edges for -FMT
tbl_edges<- cluster_network %>% filter(MouseGroup == 'Jax' & Significant == T) %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
      select(OTU1, OTU2, Zscore, zpadjusted) %>% 
    mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative'),
           zpadjusted=log10(1/zpadjusted)) %>%
    select(OTU1, OTU2, interaction, Zscore) %>%
    #left_join(tbl_edges_all, ., by = c('OTU1','OTU2')) %>%
    replace(is.na(.), 0) %>%
    distinct()


#Get nodes found in -FMT

tbl_nodes <- rbind(cluster_network %>% filter(MouseGroup == 'Jax') %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% select(OTU1, Family_OTU1)%>% distinct(),
    cluster_network %>% filter(MouseGroup == 'Jax') %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
   mutate(OTU2 = gsub('Otu', '', .$OTU2)) %>% select(OTU1=OTU2, Family_OTU1=Family_OTU2)%>% distinct()) %>% 
    mutate(alpha = 1) %>% distinct() %>% left_join(., filter(Instances, MouseGroup == 'Jax'), by = 'OTU1') %>%
    select(-MouseGroup) %>% mutate(total_instances = as.numeric(total_instances)) %>%
  left_join(tbl_nodes_all, ., by = 'OTU1') %>% 
  mutate(Family_OTU1 = ifelse(is.na(Family_OTU1), 'Undetermined', Family_OTU1)) %>%
  replace(is.na(.), .01) %>% distinct() %>% select(-alpha) %>%
  left_join(., filter(Instances_new, MouseGroup == 'Jax'))


#Find missing taxa & remove their edges
missing_taxa <- tbl_nodes %>% filter(alpha == .01) %>% select(OTU1) %>% mutate(OTU2=OTU1)

tbl_edges <- tbl_edges %>% anti_join(., missing_taxa, 'OTU1') %>% anti_join(., missing_taxa, 'OTU2')

#merge node and edge data
graph_nodes <- graph_from_data_frame(tbl_edges, tbl_nodes, directed = T) %>% 
    delete_vertices(., V(.)$name == 27 | V(.)$name == 49 | V(.)$name == 68 | 
                      V(.)$name == 95 | V(.)$name == 73)

#graph just nodes
nodes <- ggraph(graph_nodes, layout = 'circle') +
   geom_edge_link(aes(
                      edge_width = abs(Zscore)*.001, 
                       alpha = abs(Zscore), 
                       edge_color = interaction),) +
      scale_edge_width(
                       aes((Zscore)),
                       range = c(.001, 2)
                       ) +
    scale_edge_color_manual(values = c('navyblue','firebrick')) +
  #geom_node_point(aes(size = prop_OTU, alpha = alpha), color = 'black') +
  geom_node_point(aes( size = prop_OTU*.6, color = Family, alpha = alpha)) +
  scale_color_manual(values = bugColors) +
     scale_size(range = c(.001,11)) +
  labs(color = 'Order', 
         title = "Jax") +
    theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'none') 

a <- nodes + geom_node_text(aes(label = name), size = 3,  nudge_x = nodes$data$x * .3, nudge_y = nodes$data$y * .3, check_overlap=FALSE)
a
# Env

#Get nodes found in Env



#Now layer edges for Env
tbl_edges<- cluster_network %>% filter(MouseGroup == 'Env' & Significant == T) %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
      select(OTU1, OTU2, Zscore, zpadjusted) %>% 
    mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative'),
           zpadjusted=log10(1/zpadjusted)) %>%
    select(OTU1, OTU2, interaction, Zscore) %>%
    #left_join(tbl_edges_all, ., by = c('OTU1','OTU2')) %>%
    replace(is.na(.), 0) %>%
    distinct()


#Get nodes found in Env

tbl_nodes <- rbind(cluster_network %>% filter(MouseGroup == 'Env') %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% select(OTU1, Family_OTU1)%>% distinct(),
    cluster_network %>% filter(MouseGroup == 'Env') %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
   mutate(OTU2 = gsub('Otu', '', .$OTU2)) %>% select(OTU1=OTU2, Family_OTU1=Family_OTU2)%>% distinct()) %>% 
    mutate(alpha = 1) %>% distinct() %>% left_join(., filter(Instances, MouseGroup == 'Jax'), by = 'OTU1') %>%
    select(-MouseGroup) %>% mutate(total_instances = as.numeric(total_instances)) %>%
  left_join(tbl_nodes_all, ., by = 'OTU1') %>% 
  mutate(Family_OTU1 = ifelse(is.na(Family_OTU1), 'Undetermined', Family_OTU1)) %>%
  replace(is.na(.), .01) %>% distinct() %>% select(-alpha) %>%
    left_join(., filter(Instances_new, MouseGroup == 'Env'))


#Find missing taxa & remove their edges
missing_taxa <- tbl_nodes %>% filter(alpha == .01) %>% select(OTU1) %>% mutate(OTU2=OTU1)

tbl_edges <- tbl_edges %>% anti_join(., missing_taxa, 'OTU1') %>% anti_join(., missing_taxa, 'OTU2')


#merge node and edge data
graph_nodes <- graph_from_data_frame(tbl_edges, tbl_nodes, directed = T) %>% 
    delete_vertices(., V(.)$name == 27 | V(.)$name == 49 | V(.)$name == 68 | 
                      V(.)$name == 95 | V(.)$name == 73)
#graph just nodes
nodes <- ggraph(graph_nodes, layout = 'circle') +
   geom_edge_link(aes(
                      edge_width = abs(Zscore)*.001, 
                       alpha = abs(Zscore), 
                       edge_color = interaction),) +
      scale_edge_width(
                       aes((Zscore)),
                       range = c(.01, 2)
                       ) +
    scale_edge_color_manual(values = c('navyblue','firebrick')) +
  #geom_node_point(aes(size = prop_OTU, alpha = alpha), color = 'black') +
  geom_node_point(aes( size = prop_OTU*.6, color = Family,alpha = alpha)) +
  scale_color_manual(values = bugColors) +
     scale_size(range = c(.001,11)) +
  scale_color_manual(values = bugColors) +
  labs(color = 'Order', 
         title = "Env") +
    theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'none') 

b <- nodes + geom_node_text(aes(label = name), size = 3,  nudge_x = nodes$data$x * .3, nudge_y = nodes$data$y * .3, check_overlap=FALSE)
b

# +FMT

#Now layer edges for +FMT
tbl_edges<- cluster_network %>% filter(MouseGroup == 'Env2Jax'& Significant == T) %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
      select(OTU1, OTU2, Zscore, zpadjusted) %>% 
    mutate(interaction = ifelse(Zscore > 0, 'Positive', 'Negative'),
           zpadjusted=log10(1/zpadjusted)) %>%
    select(OTU1, OTU2, interaction, Zscore) %>%
    #left_join(tbl_edges_all, ., by = c('OTU1','OTU2')) %>%
    replace(is.na(.), 0) %>%
    distinct()


#Get nodes found in +FMT

tbl_nodes <- rbind(cluster_network %>% filter(MouseGroup == 'Env2Jax') %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
mutate(OTU1 = gsub('Otu', '', .$OTU1)) %>% select(OTU1, Family_OTU1)%>% distinct(),
    cluster_network %>% filter(MouseGroup == 'Env2Jax') %>%
    filter(Class_OTU1 == 'Clostridia' & Class_OTU2 == 'Clostridia') %>%
   mutate(OTU2 = gsub('Otu', '', .$OTU2)) %>% select(OTU1=OTU2, Family_OTU1=Family_OTU2)%>% distinct()) %>% 
    mutate(alpha = 1) %>% distinct() %>% left_join(., filter(Instances, MouseGroup == 'Jax'), by = 'OTU1') %>%
    select(-MouseGroup) %>% mutate(total_instances = as.numeric(total_instances)) %>%
  left_join(tbl_nodes_all, ., by = 'OTU1') %>% 
  mutate(Family_OTU1 = ifelse(is.na(Family_OTU1), 'Undetermined', Family_OTU1)) %>%
  replace(is.na(.), .01) %>% distinct() %>% select(-alpha) %>%
    left_join(., filter(Instances_new, MouseGroup == 'Env2Jax'))

#Find missing taxa & remove their edges
missing_taxa <- tbl_nodes %>% filter(alpha == .01) %>% select(OTU1) %>% mutate(OTU2=OTU1)

tbl_edges <- tbl_edges %>% anti_join(., missing_taxa, 'OTU1') %>% anti_join(., missing_taxa, 'OTU2')


#merge node and edge data
graph_nodes <- graph_from_data_frame(tbl_edges, tbl_nodes, directed = T) %>% 
    delete_vertices(., V(.)$name == 27 | V(.)$name == 49 | V(.)$name == 68 | 
                      V(.)$name == 95 | V(.)$name == 73)
#graph just nodes
nodes <- ggraph(graph_nodes, layout = 'circle') +
   geom_edge_link(aes(
                      edge_width = abs(Zscore)*.001, 
                       alpha = abs(Zscore), 
                       edge_color = interaction),) +
      scale_edge_width(
                       aes((Zscore)),
                       range = c(.01, 2)
                       ) +
    scale_edge_color_manual(values = c('navyblue','firebrick')) +
  #geom_node_point(aes(size = prop_OTU, alpha = alpha), color = 'black') +
  geom_node_point(aes( size = prop_OTU*.6, color = Family,alpha = alpha)) +
  scale_color_manual(values = bugColors) +
     scale_size(range = c(.001,11)) +
  scale_color_manual(values = bugColors) +
  labs(color = 'Order', 
         title = "Env2Jax") +
    theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'none') 


c <- nodes + geom_node_text(aes(label = name), size = 3,  nudge_x = nodes$data$x * .3, nudge_y = nodes$data$y * .3, check_overlap=FALSE)
c

leg <- cowplot::get_legend(ggraph(graph_nodes, layout = 'circle') + 
    geom_edge_link(aes(edge_width = Zscore), alpha =.4) +
    scale_edge_width_continuous(range = c(0,5)) +
    geom_node_point(size = 14, aes(color = Family_OTU1)) +
    scale_color_manual(values = bugColors) +labs(color = 'Order') +
      theme(panel.background = element_blank(),
          legend.text = element_text(size = 12),
          plot.title = element_text(hjust = 0.5, size = 16),
          legend.key = element_blank(),
          legend.position = 'bottom'))
    

temp <- cowplot::plot_grid(a,c,b,  nrow = 1)
temp
ggsave("../figs/fig5/5E_InteractionNetworks_Lachno.png", width = 8,height = 2.8)
ggsave("../figs/fig5/5E_InteractionNetworks_Lachno.pdf", width = 8,height = 2.8)

cowplot::plot_grid(leg)
ggsave("../figs/fig5/5E_InteractionNetworks_Lachno_leg.png", width = 14,height = 2.8)
ggsave("../figs/fig5/5E_InteractionNetworks_Lachno_leg.pdf", width = 14,height = 2.8)
cowplot::plot_grid(temp, leg, nrow = 2)
```





Are interactions occuring between Env taxa or Env-recipient or recipient-recipient
```{r}

#uncomment lines to separate engrafted vs unengrafted microbes
temp <- PrevalentSets %>% 
  filter(Significant == T) %>% 
  mutate(interaction_type = ifelse(Zscore > 0, 'Positive', 'Negative')) %>%
  select(MouseGroup, OTU1Type, OTU2Type,OTU1, OTU2,Class_OTU1, Class_OTU2, interaction_type) %>%
  mutate(interaction = NA) %>% 
  distinct() %>%
  mutate(interaction = ifelse(OTU1Type == 'Donor Taxa' & OTU2Type == 'Donor Taxa', 'Env-Env', interaction),
         interaction = ifelse(OTU1Type == 'Recipient Taxa' & OTU2Type == 'Recipient Taxa', 'Jax-Jax', interaction),
         interaction = ifelse(OTU1Type == 'Donor Taxa' & OTU2Type == 'Recipient Taxa', 'Env-Jax', interaction),
         interaction = ifelse(OTU1Type == 'Donor Taxa' & OTU2Type == 'Shared Taxa', 'Env-shared', interaction),
         interaction = ifelse(OTU1Type == 'Recipient Taxa' & OTU2Type == 'Shared Taxa', 'Jax-shared', interaction),
         interaction = ifelse(OTU1Type == 'Shared Taxa' & OTU2Type == 'Shared Taxa', 'shared-shared', interaction)) %>% na.omit() 


#how many interactions for each?
num_ints <- (temp %>% group_by(MouseGroup, interaction_type) %>% 
  mutate(num_interactions = n()) %>% ungroup %>%
  select(MouseGroup, num_interactions,interaction_type) %>% distinct()) %>% group_by(MouseGroup) %>% mutate(prop_interactions = num_interactions/sum(num_interactions)) %>% ungroup()
num_ints

temp$interaction <- factor(temp$interaction, levels=c("Env-Env", "Jax-Jax", "Env-Jax", "Env-shared", "Jax-shared", "shared-shared")) 
#What types of interactions do we see

#Normalized interactions
temp %>% left_join(., num_ints) %>% group_by(interaction, interaction_type, MouseGroup) %>% 
  mutate(num_type_interactions = n(), 
         scaled_interactions = num_type_interactions/num_interactions) %>% ungroup() %>%
  select(MouseGroup, scaled_interactions, interaction_type, interaction) %>% distinct() %>%
  ggplot(., aes(x=interaction, y=scaled_interactions, fill =interaction_type)) + 
  geom_bar(stat = 'identity', position = 'stack') + 
  scale_fill_manual(values = c('#f7941d','#27aae1')) +
  labs(x= 'Co-association Pair', y = 'Proportion of Co-associations', fill = 'Co-association') +
  theme_clean() + 
  facet_wrap(~MouseGroup, nrow = 3, strip.position = 'right') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 16),
        axis.text.y = element_text(size=16, color = 'black'),
        axis.title.x.bottom = element_text(size = 16,color = 'black'),
        axis.title.y.left = element_text(size = 16,color = 'black'),
        legend.position = 'right')

ggsave("../figs/s6/s6_ALLInteractionCounts.png", width = 5, height = 5)
ggsave("../figs/s6/s6_ALLInteractionCounts.pdf", width = 5, height = 5)

#Sheer # of interactions
temp %>% #filter(interaction != 'Env-Env' & interaction != 'Env-recipient' & interaction != 'recipient-recipient') %>% 
  ggplot(., aes(x=interaction, fill =interaction_type)) + 
  geom_bar(stat = 'count', position = 'stack') + 
  scale_fill_manual(values = c('#f7941d','#27aae1')) +
  labs(x= 'Co-association pair', y = '# of Interactions', 
       fill = 'Interaction Type') +
  theme_clean() + 
  facet_wrap(~factor(MouseGroup, levels = c('Jax', 'Env2Jax', 'Env')), nrow = 3, strip.position = 'top', scales = 'free_y') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 10),
        axis.text.y = element_text(size=10, color = 'black'),
        axis.title.x.bottom = element_text(size = 12,color = 'black'),
        axis.title.y.left = element_text(size = 12,color = 'black'),
        legend.position = 'right', strip.text = element_text(size = 12))

ggsave("../figs/s7/s7_ALLInteractionCounts.png", width = 5, height = 5)
ggsave("../figs/s7/s7_ALLInteractionCounts.pdf", width = 5, height = 5)
#ggsave("../figs/fig5/5X_InteractionCounts.png", width = 5, height = 2.5)
#ggsave("../figs/fig5/5X_InteractionCounts.pdf", width = 5, height = 2.5)

```

What is distribution of number of interactions amongst OTUs?
```{r}
df <- rbind(
  temp %>% select(MouseGroup, 'OTU'=OTU1),
  temp %>% select(MouseGroup, 'OTU'=OTU2)) %>% 
  group_by(MouseGroup, OTU) %>% mutate(num_OTU_interactions = n()) %>% 
  ungroup %>% distinct() 
  
  
ggplot(df, aes(num_OTU_interactions, fill = MouseGroup)) + 
  geom_histogram(bins = 10, color = 'black') + facet_wrap(~MouseGroup) + theme_cowplot() + geom_density()
  
```


Interesting, preFMT - specific communities don't interact much! Universal microbes do interact in all communities. Env microbes also are able to interact with shared bugs, who are these interactors?


Now let's do Class split by interaction type
```{r}

temp_2 <- rbind(select(temp, MouseGroup, OTU1, OTU2, Class_OTU1, Class_OTU2, interaction_type), 
  (select(temp, MouseGroup, 'OTU1'='OTU2', 'OTU2'='OTU1', 'Class_OTU2'='Class_OTU1', 'Class_OTU1'='Class_OTU2', interaction_type))) %>% distinct() %>% 
  group_by(MouseGroup, Class_OTU1, Class_OTU2, interaction_type) %>% 
  mutate(num_interactors = n()) %>% ungroup() %>% select(-OTU1, -OTU2) %>% 
  mutate(num_interactors = as.numeric(num_interactors)) %>% distinct() %>%
  mutate(num_interactors = ifelse(Class_OTU1 == Class_OTU2, num_interactors/2, num_interactors)) #since made mirror, need to remove the ones that are duplicates

#get coordinates for background
grid <- rbind(data.frame(Class_OTU1=temp$Class_OTU1), data.frame(Class_OTU1=temp$Class_OTU2)) %>% 
  distinct() %>% 
  mutate(merge = 'merge')

grid <- rbind(mutate(grid, MouseGroup='Jax'),
      mutate(grid, MouseGroup='Env2Jax'),
      mutate(grid, MouseGroup='Env'))

grid <- left_join(grid, grid, by = c('merge', 'MouseGroup')) %>% 
  dplyr::rename('Class_OTU1'='Class_OTU1.x', 'Class_OTU2'='Class_OTU1.y') %>% 
  left_join(., temp_2, 
              by = c('Class_OTU1', 'Class_OTU2', 'MouseGroup')) 

#add scaler
scaled_temp_2 <- temp_2 %>% select(Class_OTU1, Class_OTU2, MouseGroup, num_interactors, interaction_type) %>%
  left_join(.,
            read.csv("../tables/MaPS-Seq_ClassCounts.csv") %>% 
              rename('Class_OTU1' = 'Class', 'num_class_1' = 'num_class'), by = c('MouseGroup', 'Class_OTU1')) %>% left_join(., 
            read.csv("../tables/MaPS-Seq_ClassCounts.csv") %>% 
              rename('Class_OTU2' = 'Class', 'num_class_2' = 'num_class'), by = c('MouseGroup', 'Class_OTU2')) %>% 
        mutate(num_mates = ifelse(Class_OTU1 == Class_OTU2, (num_class_1*num_class_2)-1, num_class_1*num_class_2),
               scaled_num_interactors = num_interactors/num_mates) %>% na.omit                                                                                                                       



#scaled_temp_2 
temp_2 %>% filter(interaction_type == 'Negative') %>%
 distinct() %>%
  distinct() %>%
   ggplot(., aes(x=Class_OTU1, y = Class_OTU2)) +
    geom_tile(data = grid, aes(x=Class_OTU1, y = Class_OTU2), color = 'black', fill = NA) +
  geom_tile(aes(fill = num_interactors), color = 'black') +
    scale_fill_gradient(low='lightblue', high='navyblue') +
facet_grid(~factor(MouseGroup, levels = c('Jax', 'Env2Jax', 'Env'))) +
  labs(fill = '# of - associations') +
  theme_cowplot() +     
 # geom_text(aes(label=paste(signif(scaled_num_interactors, 2)*100, '%', sep = '')), 
  #              size = 2.5, color = 'white') +
   geom_text(aes(label=num_interactors), 
                size = 2.5, color = 'white') +
  labs(y = 'Class', x = 'Class', title = 'Interactions with Shared Taxa') +
    theme(axis.text.x = element_text(size=9,color = 'black', 
                                     angle = 45, hjust = 1), 
        axis.text.y = element_text(size=9, color = 'black'),
        axis.title.x.bottom = element_text(size = 14,color = 'black'),
        axis.title.y.left = element_text(size = 14,color = 'black'),
        legend.text = element_text(size=10,color = 'black'),
        legend.title = element_text(size = 12, hjust = .5,color = 'black'),
        legend.position = 'bottom',
        strip.background = element_blank())
        

ggsave("../figs/fig5/5D_ClassInteractions_neg.pdf", width = 7.5, height = 4)

#scaled_temp_2 
temp_2 %>% filter(interaction_type == 'Positive') %>%
 distinct() %>%# filter(MouseGroup != 'Env') %>%
  distinct() %>%
   ggplot(., aes(x=Class_OTU1, y = Class_OTU2)) +
    geom_tile(data = grid, aes(x=Class_OTU1, y = Class_OTU2), color = 'black', fill = NA) +
  geom_tile(aes(fill = num_interactors), color = 'black') +
  facet_grid(~factor(MouseGroup, levels = c('Jax', 'Env2Jax', 'Env'))) +
  labs(fill = '# of + associations') +
    scale_fill_gradient(low='#FFCCCB', high='firebrick3') +
  theme_cowplot() + 
     geom_text(aes(label=num_interactors), 
                size = 2.5, color = 'white') +
#geom_text(aes(label=paste(signif(scaled_num_interactors, 2)*100, '%', sep = '')), 
#                size = 2.5, color = 'white') +  
  labs(y = 'Class', x = 'Class', title = 'Associations with Shared Taxa') +
    theme(axis.text.x = element_text(size=9,color = 'black', 
                                     angle = 45, hjust = 1), 
        axis.text.y = element_text(size=9, color = 'black'),
        axis.title.x.bottom = element_text(size = 14,color = 'black'),
        axis.title.y.left = element_text(size = 14,color = 'black'),
        legend.text = element_text(size=10,color = 'black'),
        legend.title = element_text(size = 12, hjust = .5,color = 'black'),
        legend.position = 'bottom',
        strip.background = element_blank())
        

ggsave("../figs/fig5/5D_ClassInteractions_pos.pdf", width =7.5, height = 4)



##add Class abundance over tile plots

read.csv("../tables/MaPS-Seq_ClassCounts.csv") %>% 
  ggplot(., aes(x=Class, y = num_class)) + 
  geom_bar(color = 'black', fill = 'gray80', stat = 'identity') + 
  labs(y='# OTUs in Class', x= '') + theme_clean() +
  theme(axis.text.y = element_text(size=10),
        axis.text.x = element_blank(),
        axis.title = element_text(size = 12), 
        strip.background = element_blank()) + 
  facet_wrap(~factor(MouseGroup, levels = c('Jax', 'Env2Jax', 'Env')))

ggsave("../figs/fig5/5B.3_ClassOTUCounts.pdf", width = 6, height = 1.25)


```



#Are engrafting microbes the ones with most interactions? Number of interactions within donor predicts success in recipient?

```{r}
#What happens to Env microbes?
group <- 'Env'

engrafted_Envs <- 
  rbind(PrevalentSets %>% #need to flip Prevalent sets so interactions go both ways correct
  filter(MouseGroup == group & zpadjusted < .05) %>% #& OTU1Type != 'Recipient Taxa') %>% 
    select(OTU1, OTU2),
    rbind(PrevalentSets %>% #need to flip Prevalent sets so interactions go both ways correct
  filter(MouseGroup == group & zpadjusted < .05) %>%# & OTU2Type != 'Recipient Taxa') %>% 
    select(OTU1=OTU2, OTU2=OTU1))) %>%  filter(OTU1!=OTU2)%>% distinct() %>% select(OTU1) %>%
  group_by(OTU1) %>% mutate(num_interactions = n()) %>% 
  select(OTU1, num_interactions) %>% 
  left_join(filter(otumapping, OTUType !='NA')%>% select(OTU1=OTU, emergence, OTUType, baseMean,log2FoldChange), .) %>%
  distinct() 

engrafted_Envs$num_interactions[is.na(engrafted_Envs$num_interactions)] <- 0 

corr <- cor.test((engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$log2FoldChange, (engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$num_interactions, method = 'spearman',exact=FALSE)$estimate
pval <-  cor.test((engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$log2FoldChange, (engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$num_interactions, method = 'spearman',exact=FALSE)$p.value


engrafted_Envs %>% filter(OTUType == 'Donor Taxa') %>%
  ggplot(., aes(x=log2FoldChange, y = num_interactions), color = 'black') +
  #ggplot(., aes(x=baseMean*log2FoldChange, y = num_interactions)) +
  geom_point(size = 2) + geom_smooth(method = 'lm') + theme_cowplot() +# facet_wrap(~OTUType) +
  annotate('text', x = .8, y = 60, label = paste('R2 = ', signif(corr, 2), ', p = ', signif(pval, 2), sep = ''), size = 5) +
  labs(title = 'Donor Specific OTUs', x = 'log2(Fold Change in Recipient)', y = 'Number of interactions in Donor')

ggsave("../figs/fig5/5D_DonorOutcomes_correlations.pdf", width = 4, height = 4)


#cor.test((engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$log2FoldChange, (engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$num_interactions, method = 'spearman',exact=FALSE)

#cor.test(engrafted_Envs$baseMean*engrafted_Envs$log2FoldChange, engrafted_Envs$num_interactions, method = 'spearman', exact=FALSE)

```


ABUNDANCE IN ENV2JAX CORRELATED WITH THEIR NUMBER OF INTERACTIONS
```{r}

group <- 'Env2Jax'

engrafted_Envs <- 
  rbind(PrevalentSets %>% #need to flip Prevalent sets so interactions go both ways correct
  filter(MouseGroup == group & zpadjusted < .05) %>%# & OTU1Type != 'Recipient Taxa') %>% 
    select(OTU1, OTU2),
    rbind(PrevalentSets %>% #need to flip Prevalent sets so interactions go both ways correct
  filter(MouseGroup == group & zpadjusted < .05) %>% # & OTU2Type != 'Recipient Taxa') %>% 
    select(OTU1=OTU2, OTU2=OTU1))) %>%  filter(OTU1!=OTU2)%>% distinct() %>% select(OTU1) %>%
  group_by(OTU1) %>% mutate(num_interactions = n()) %>% 
  select(OTU1, num_interactions) %>% left_join(filter(otumapping, OTUType !='NA')%>% select(OTU1=OTU, emergence, OTUType, baseMean,log2FoldChange), .) %>%
  distinct() 

engrafted_Envs$num_interactions[is.na(engrafted_Envs$num_interactions)] <- 0 


engrafted_Envs %>% filter(OTUType != 'Recipient Taxa') %>%
  ggplot(., aes(factor(emergence, levels = c('depleted', 'unchanged', 'enriched')), 
                                   num_interactions)) + 
  stat_boxplot(geom='errorbar', width = .1) +
  geom_boxplot(notchwidth = .2, outlier.shape = NA, width = .4, fill = 'white') +
    geom_jitter(alpha = .2) + 
  theme_cowplot() +
  ggsignif::geom_signif(
    comparisons = list(c('depleted', 'unchanged'), 
                       c('unchanged', 'enriched')),
    test = 'wilcox.test',
    y_position = c(15, 30)
  ) +
  labs(x = 'Env Strain FMT Outcome', y = '# of Interactions in Env2Jax', fill =NA) + 
  theme(axis.text.x = element_text(size=16,color = 'black', angle = 45, hjust = 1), 
        axis.text.y = element_text(size=16, color = 'black'),
        axis.title.x.bottom = element_text(size = 16,color = 'black'),
        axis.title.y.left = element_text(size = 16,color = 'black'),
        legend.text = element_text(size=12,color = 'black'),
        legend.title = element_text(size = 14, hjust = .5,color = 'black'),
        legend.position = 'none') 

ggsave("../figs/fig5/5Dalt_FMTOutcomes.pdf", width = 3, height = 2.5)


```


Do bacteroides that are shared engraft better?
```{r}

group <- 'Jax'

#need to flip Prevalent sets so interactions go both ways correct
engrafted_Envs <- 
  rbind(PrevalentSets %>% filter(Class_OTU1 == 'Bacteroidia' | Class_OTU2 == 'Bacteroidia') %>% 
  filter(MouseGroup == group & zpadjusted < .05) %>% #& OTU1Type != 'Recipient Taxa') %>% 
    select(OTU1, OTU2),
    rbind(PrevalentSets %>% filter(Class_OTU1 == 'Bacteroidia' | Class_OTU2 == 'Bacteroidia') %>%
  filter(MouseGroup == group & zpadjusted < .05) %>%# & OTU2Type != 'Recipient Taxa') %>% 
    select(OTU1=OTU2, OTU2=OTU1))) %>%  filter(OTU1!=OTU2)%>% distinct() %>% select(OTU1) %>%
  group_by(OTU1) %>% mutate(num_interactions = n()) %>% 
  select(OTU1, num_interactions) %>%
  left_join(filter(otumapping, OTUType !='NA')%>% select(OTU1=OTU, emergence, OTUType, baseMean,log2FoldChange) %>% left_join(., select(Tax_Table, OTU1=OTU, Class)) %>% filter(Class == 'Bacteroidia'), .) %>%
  distinct() 

engrafted_Envs$num_interactions[is.na(engrafted_Envs$num_interactions)] <- 0 

corr <- cor.test((engrafted_Envs %>% filter(OTUType == 'Shared Taxa'))$log2FoldChange, (engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$num_interactions, method = 'spearman',exact=FALSE)$estimate
pval <-  cor.test((engrafted_Envs %>% filter(OTUType == 'Shared Taxa'))$log2FoldChange, (engrafted_Envs %>% filter(OTUType == 'Donor Taxa'))$num_interactions, method = 'spearman',exact=FALSE)$p.value

engrafted_Envs %>% filter(OTUType == 'Shared Taxa') %>%
  ggplot(., aes(x=log2FoldChange, y = num_interactions), color = 'black') +
  #ggplot(., aes(x=baseMean*log2FoldChange, y = num_interactions)) +
  geom_point(size = 2) + geom_smooth(method = 'lm') + theme_cowplot() +# facet_wrap(~OTUType) +
  annotate('text', x = .8, y = 60, label = paste('R2 = ', signif(corr, 2), ', p = ', signif(pval, 2), sep = ''), size = 5) +
  labs(title = 'Shared Bacteroides OTUs', x = 'log2(Fold Change in Recipient)', y = 'Number of interactions in Jax')

```




```{r}

group <- 'Jax'

#need to flip Prevalent sets so interactions go both ways correct
interactions <- 
  rbind(PrevalentSets %>% rename(OTU1=OTU2, OTU2=OTU1, Class_OTU1=Class_OTU2, Class_OTU2=Class_OTU1, OTU1Type=OTU2Type, OTU2Type=OTU1Type),
        PrevalentSets) %>%  filter(OTU1!=OTU2)%>% distinct() %>%
  select(OTU1, OTU2, Class_OTU1, Class_OTU2, OTU1Type, OTU2Type, Significant, Zscore, MouseGroup) %>% 
  mutate(interaction_type = ifelse(Zscore > 0, 'Positive', 'Negative'),
         interaction_type = ifelse(Significant == T, interaction_type, 'None')) %>% 
  select(-Zscore, -Significant) %>%
  distinct()

jax_interactions <- filter(interactions, MouseGroup == 'Jax') %>% rename(jax_interaction_type=interaction_type) %>% 
                    select(OTU1, OTU2, jax_interaction_type)
env_interactions <- filter(interactions, MouseGroup == 'Env') %>% rename(env_interaction_type=interaction_type) %>% 
                    select(OTU1, OTU2, env_interaction_type)

all_interactions <- filter(interactions, MouseGroup == 'Env2Jax') %>% rename(env2jax_interaction_type=interaction_type) %>% 
                        left_join(., jax_interactions, by = c('OTU1', 'OTU2')) %>%
                        left_join(., env_interactions, by = c('OTU1', 'OTU2')) %>% 
          mutate(jax_conservation = ifelse(jax_interaction_type == env2jax_interaction_type, T, F),
                 env_conservation = ifelse(env_interaction_type == env2jax_interaction_type, T, F),
                 intermicrobiome_conservation = ifelse(env_interaction_type == jax_interaction_type, T, F)) 



all_interactions %>% 
  select(Class_OTU1, Class_OTU2, env_conservation, jax_conservation, intermicrobiome_conservation) %>% 
  melt(id.vars = c('Class_OTU1', 'Class_OTU2')) %>%
  ggplot(., aes(variable, fill=value)) + geom_bar(stat = 'count') + theme_cowplot() + 
  scale_fill_manual(values = c('#ffd700','#0077be')) #+ 
  facet_grid(Class_OTU1~Class_OTU2)



```